\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\name{Vadim Gribanov}

\address{ +(48) 516 937 979 \\ mail@vadimgribanov.com \\ \href{https://github.com/yoihito}{Github} \\ \href{https://www.linkedin.com/in/yoihito/}{Linkedin } }
\address{Cracow, Poland}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}
  \begin{rSection}{Summary}
    {I'm a software engineer who loves to create awesome products that meet user needs. I have more than nine years of experience and a track record of delivering successful products. When faced with complex technical problems, I have a knack for troubleshooting and analyzing issues. I work well with others and value open communication. I'm comfortable working in fast-paced environments. Learning new skills is a passion of mine, and I'm always looking for opportunities to improve my knowledge and expertise. Also, I'm pretty strong in algorithms - I've even won some national olympiads in informatics}
  \end{rSection}

  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming Languages & Ruby, Go, NodeJS, Python \\
      Frameworks            & Ruby on Rails, Echo, NestJS, ExpressJS, VueJS, Django, FastAPI, React \\
      Test frameworks       & Jest, RSpec \\
      Databases             & PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
      Cloud                 & AWS, GCP, Azure \\
      Web                   & HTML5, CSS3 \\
      CI                    & Github Actions, CircleCI \\
      Methodologies         & Scrum, Kanban, OOP, Domain Driven Design, SOLID, GRASP, TDD \\
      Other                 & Git, Kubernetes, Terraform, Docker, ElasticSearch, \\
                            & Twilio, Firebase, Wells Fargo API, Intacct Sage API \\
    \end{tabular}
  \end{rSection}

  \begin{rSection}{Experience}
    \begin{rSubsection}{Peer Street, Inc. (Los Angeles, CA)}{June 2018 - February 2023}{Senior Software Engineer(Independent Contractor)}{Remote}
    \item Designed and implemented a financial product, that helped to attract over \$3000000 of new investments in 5 months
    \item Implemented banking integration to simplify our operations with customers, which in turn increased number of customers' transactions by 44\%.
    \item Automated financial operations which lead to saving 20 hours per day for servicing department on average. These changes led to reduced servicing error rate by 20\% and to increased overall revenue by 7\%.
    \item Improved financial data consistency, reduced data loss by processing customers' operations in a transactional way. This change gave us a better observability, reduced time required to make data correction requests by 50\%
    \item Promoted Domain Driven Design and Clean Code approach to improve our design/development process, as well as platform maintance
    \item Reviewed code and helped trend set high quality standards for other engineers.
    \item Gave fast feedback to product managers about upcoming features complexity.
    \end{rSubsection}

    \begin{rSubsection}{Silicon Valley Software Group LLC (San Francisco, CA)}{March 2016 - April 2018}{Software Engineer(Independent Contractor)}{Remote}
    \item Leaded a team of three frontend developers.
    \item Designed and developed multiple complex frontend application from scratch using React and Node.
    \item Promoted unit tests and integration tests. As a result, we increased stability of the application.
    \item Setup automated code reviews with linters and configured CI/CD pipeline using TravisCI, CircleCI and GithubActions.
    \item Reviewed code and mentored other devs.
    \item Improved code quality of multiple projects after active development
    \item Configured production server to serve frontend assets from CDN.
    \end{rSubsection}

    \begin{rSubsection}{Appcast Inc. (Boston, MA)}{October 2015 - February 2016}{Ruby on Rails Developer}{Minsk, Belarus}
    \item Implemented API service built on Ruby on Rails.
    \item Refactored and optimised Cost Per Action estimation algorithm.
    \item Implemented UI features in web application built on Angular.
    \end{rSubsection}

    \begin{rSubsection}{SivinTech LLC}{December 2014 - September 2015}{Ruby on Rails developer}{Minsk, Belarus}
    \item Designed and implemented call center for the client of SivinTech. Used Twilio as communication platform.
    \item Migrated old Java applet to Angular.
    \end{rSubsection}
  \end{rSection}

  \begin{rSection}{Education}
    {\bf Belarusian State University Of Informatics and Radioelectronics, Minsk} \hfill {\em 2013 - 2017} \\
    { Faculty of Computer Systems and Networks } \\
    { B.S. in Computer Science \& Software Engineering } \\
    {\bf Belarusian State University Of Informatics and Radioelectronics, Minsk} \hfill {\em 2017 - 2020} \\
    { Faculty of Computer Systems and Networks } \\
    { M.S. in Computer Science } \\
    { incomplete degree } \\
  \end{rSection}

  \begin{rSection}{Honors \& Awards}
  {Competed in RuCTF 2015 competition as part of the team from our university. Our team took 2nd place.} \\
  {Competed in Belarus National Olympiad in Informatics in 2013. Took 1st degree diploma.} \\
  {Competed in Individual Olympaid in Informatics and Programming in 2013. Took awardee diploma.} \\
  {Competed in Belarus National Olympiad in Informatics in 2012. Took 2nd degree diploma.} \\
  {Competed in Belarus National Olympiad in Informatics in 2011.}
  \end{rSection}

  \begin{rSection}{Links}
  \item \href{https://github.com/yoihito}{Github - https://github.com/yoihito}
  \item \href{https://www.linkedin.com/in/yoihito/}{Linkedin - https://www.linkedin.com/in/yoihito/}
  \end{rSection}

\end{document}
